Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/hotspots-paper.Rmd
fixed code chunks with child arg

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 1, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::html_document2: 
    code_folding: hide
  bookdown::pdf_document2:
    fig_caption: true
---

```{r child = "abstract.Rmd"}
```

```{r child="intro.Rmd"}
```

@@

```{r child="methods.Rmd"}
```

@@

### Chr 5 index v position plot

@@

```{r read_discussion, child = "results.Rmd"}
```

```{r read_discussion, child = "discussion.Rmd"}
```

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "August 1, 2019"
bibliography: research.bib
linkReferences: true
link-citations: true 
output: 
  bookdown::pdf_document2:
    fig_caption: true
  bookdown::html_document2: 
    code_folding: hide
---

```{r child = "abstract.Rmd", eval = TRUE}
```

```{r child="intro.Rmd", eval = TRUE}
```

@@

```{r child="methods.Rmd", eval = TRUE}
```

@@

@@

```{r read_results, child = "results.Rmd", eval = TRUE}
```

```{r read_discussion, child = "discussion.Rmd", eval = TRUE}
```
